---
title: "figures"
author: "Clint McKenna"
date: "4/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## data prep
```{r, message = FALSE}
# load packages
library(tidyverse)

# custom functions
# dplyr select
select <- dplyr::select

# read in data seperately
dat <- read_csv('../data/data.csv')
rounds <- read_csv('../data/rounds.csv')
edgelist <- read_csv('../data/edgelist.csv')

```


## ggplot scores by condition
```{r}
# make new variable that recodes 'correct' as 'misinfo endorsed'
rounds <- rounds %>%
  mutate(misinfo = 1 - correct)


# make simple plot
p <- rounds %>%
  filter(!is.na(congenialMisinfo)) %>%
  ggplot(., aes(x = round, y = misinfo, group = survey, color = survey, fill = survey)) +
    geom_point(position = position_jitter(height = 0.05, width = 0.2), 
               alpha = .7) +
    stat_smooth(method = 'glm', 
                formula = y ~ x, 
                aes(fill = survey, alpha = .5),
                alpha = 0.2, size = 1) +
    scale_color_manual(values = c('#3b5998', 'red'), na.value = 'light grey') +
    scale_fill_manual(values = c('#3b5998', 'red'), na.value = 'light grey') +
    facet_grid(~ congenialMisinfo + moralCondition) +
    theme_bw()


# output p
p

```























Each point is a participant. Each individual has a point at each of the four time points. Jitter makes the points scatter a little bit, so you can see how the grouping of individual points looks like.

We can also style the points a little more, like adjusting the size and transparency (alpha)

```{r}
p <- rounds %>%
  ggplot(., aes(x = round, y = score, color = condition, group = condition)) +
    geom_point(position = position_jitter(height = 0.05, width = 0.2),
               size = 2.5,
               alpha = .5) 
p

```


Now, we can add layers and fix some things in following steps.

First, its usually good to scale the y-axis to show the whole range of values (otherwise it looks misleading).
```{r}

# limits arguemnt is upper and lower bound for y-axis
p <- p +
  scale_y_continuous(limits = c(1, 5))

p

```

we can also change the colors. The aes value was assigned to condition. This function can be used to specify specific we might want to use.
```{r}

p <- p +
  scale_color_manual(values = c('#FFCB05', '#00274C'))

p

```

and add labels
```{r}
p <- p +
  labs(
    title = 'Scores by Round Number',
    y = 'Response Score',
    x = 'Round Number',
    color = 'Condition',
    subtitle = 'Results based on 2 experimental networks',
    caption = 'Based on limited data')

p
```

and theres also some themes that are built-in to ggplot2. I often use theme_bw()
```{r}
p <- p +
  theme_bw()

p
```


we can save this plot by running the following lines all at once.
```{r}
png('../figures/scores.png', units = 'in', width = 8, height = 6, res = 750)
p
dev.off()


```


## text data
Just for fun, lets also look at some of the messages that were sent.

```{r}
# lots of the responses are repeated, so just get the unique entries
text <- rounds$response %>%
  unique()

head(text)



```

a nice overview of text data can be made with a wordcloud
```{r}

library(tm)
library(wordcloud)

# convert text to a corpus
text <- Corpus(VectorSource(text))

# do some basic cleaning of text
text <- text %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(tolower) %>%
  tm_map(removeWords, stopwords('english'))

# create term document matrix
tdm <- TermDocumentMatrix(text) 
tdmMatrix <- as.matrix(tdm) 
words <- sort(rowSums(tdmMatrix), decreasing=TRUE) 
datMatrix <- data.frame(word = names(words), freq = words)

# print and save wordcloud
png('../figures/wordcloud.png', units="in", width=6, height=6, res=750)
wordcloud(
  words = datMatrix$word,
  max.words = Inf,
  freq = datMatrix$freq,
  min.freq = 1,
  random.order = FALSE,
  color = brewer.pal(9, 'Blues')[(5:9)],
  rot.per=0.15, 
  scale = c(3.5, 0.1))

dev.off()


```



